---
title: "report"
author: "Nils Brun"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This Project aimed to understand and analyze the bias in the media coverage of
conflict happening in gaza. 
Using the swissdox API of the LiRi (Linguistic Research Infrastructure) of the University of Zurich, i got access to the data of the SRF (Schweizer Radio und Fernsehen) news articles in the time frame of the 7. october 2023 to the 21. may 2024. The specific time frame was chosen, due to the attacks of Hamas on Israel 
at the beginning of this new stage of the conflict.

# Hypothesis
The hypothesis of this project suggests, that the media coverage is not only slanted towards more visibility
for the israeli side, but also that the media coverage is biased in the way that it is more likely to use
negative words when talking about the palestinian side.

Therefore the hypothesis of this short capstoneproject are the following:
1. The media coverage of SRF gives more visibility to the israeli side
2. The media coverage of SRF is negatively slanted towards the palestinian side

# Data gathering, preparation and plotting
## Data gathering
Unfortunately the documentation of the API was only for python. While my attempts on translating the code to R were not successful (this can be seen in the junk folder), i decided to use a jupiter notebook with python to gather the data. The data was then saved as a tsv file and loaded into R. 
The jupiter notebook can be found in the data folder.

## Data preparation
```{r, eval=F}
#load data
library(readr)
data_srf <- read_tsv("../data/dataset.tsv")

#make the "head" and "content" column lowercase
data_srf$head_lower <- tolower(data_srf$head)
data_srf$content_lower <- tolower(data_srf$content)

#change the formate of the pubtime variable
data_srf$pubtime <- as.Date(data_srf$pubtime)

#Load the stringr package
library(stringr)

#Count the occurrences of "hamas" in each entry of the "head" and "content" column, case insensitive
data_srf$head_count_hamas <- str_count(tolower(data_srf$head), "hamas")
data_srf$content_count_hamas <- str_count(tolower(data_srf$content), "hamas")

#Count the occurrences of "israel" in each entry of the "head" and "content" column, case insensitive
data_srf$head_count_israel <- str_count(tolower(data_srf$head), "israel")
data_srf$content_count_israel <- str_count(tolower(data_srf$content), "israel")

#Count the occurrence of "Palästina" in each entry of the "head" and "content column, case insensitive
data_srf$head_count_palaestina <- str_count(tolower(data_srf$head), "palästina")
data_srf$content_count_palaestina <- str_count(tolower(data_srf$content), "palästina")

#Count the occurrence of "Gaza" in each entry of the "head" and "content column, case insensitive
data_srf$head_count_gaza <- str_count(tolower(data_srf$head), "gaza")
data_srf$content_count_gaza <- str_count(tolower(data_srf$content), "gaza")

#Count the occurence of "Genozid" in each entry of the "head" and "content" column, case insensitive
data_srf$head_count_genozid <- str_count(tolower(data_srf$head), "genozid")
data_srf$content_count_genozid <- str_count(tolower(data_srf$content), "genozid")

#Count the occurence of "Krieg" in each entry of the "head" and "content" column, case insensitive
data_srf$head_count_krieg <- str_count(tolower(data_srf$head), "krieg")
data_srf$content_count_krieg <- str_count(tolower(data_srf$content), "krieg")

#Count the occurence of "Terrorismus" in each entry of the "head" and "content" column, case insensitive
data_srf$head_count_terrorismus <- str_count(tolower(data_srf$head), "terrorismus")
data_srf$content_count_terrorismus <- str_count(tolower(data_srf$content), "terrorismus")

#save preped data
write_tsv(data_srf, "../data_prep/data_srf_prep.tsv")
```

## Data plotting
While I did some additional plots in the main.Rmd file, there will only be the more significant plots in this report. 
```{r, echo=F, message=F}
#load data
library(readr)
data_srf <- read_tsv("../data_prep/data_srf_prep.tsv")

library(ggplot2)

#Plot for "Gaza" vs "Israel"
ggplot(data_srf) +
  geom_point(aes(x = pubtime, y = content_count_gaza, color = "Content Count Gaza"), size = 1, alpha = 0.3) +
  geom_point(aes(x = pubtime, y = content_count_israel, color = "Content Count Israel"), size = 1, alpha = 0.3) +
  geom_smooth(aes(x = pubtime, y = content_count_gaza, color = "Content Count Gaza"), method = "loess", se = FALSE) +
  geom_smooth(aes(x = pubtime, y = content_count_israel, color = "Content Count Israel"), method = "loess", se = FALSE) +
  labs(x = "Publication Date", y = "Count", 
       title = "Word Count of 'Gaza' and 'Israel' in Newspaper Articles Over Time",
       color = "Legend") +
  scale_x_date(date_labels = "%B %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))


#Plot for "Krieg" vs "Genozid"
ggplot(data_srf) +
  geom_point(aes(x = pubtime, y = content_count_genozid, color = "Content Count Genozid"), size = 1, alpha = 0.3) +
  geom_point(aes(x = pubtime, y = content_count_krieg, color = "Content Count Krieg"), size = 1, alpha = 0.3) +
  geom_smooth(aes(x = pubtime, y = content_count_genozid, color = "Content Count Genozid"), method = "loess", se = FALSE) +
  geom_smooth(aes(x = pubtime, y = content_count_krieg, color = "Content Count Krieg"), method = "loess", se = FALSE) +
  labs(x = "Publication Date", y = "Count", 
       title = "Word Count of 'Genozid' and 'Krieg' in Newspaper Articles Over Time",
       color = "Legend") +
  scale_x_date(date_labels = "%B %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))


#Plot for "Hamas" vs "Palästina"
ggplot(data_srf) +
  geom_point(aes(x = pubtime, y = content_count_hamas, color = "Content Count Hamas"), size = 1, alpha = 0.3) +
  geom_point(aes(x = pubtime, y = content_count_palaestina, color = "Content Count Palästina"), size = 1, alpha = 0.3) +
  labs(x = "Publication Date", y = "Count", 
       title = "Word Count of 'Hamas' and 'Palästina' in Newspaper Articles Over Time",
       color = "Legend") +
  scale_x_date(date_labels = "%B %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

#save plot
ggsave("../figs/world_count_gaza_israel.png", width = 10, height = 6)
```

# Discussion
The first plot is a word count of the two words "gaza" and "israel". Allthough it would be hard to make a conclusion on the media coverage of both of the sides on only this plot, it is interesting to see that Israel gets consistently more mentioned than gaza

